\documentclass[margin, line]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
\usepackage{hyperref}

\setlength{\textwidth}{5.1in} % Text width of the document
\begin{document}
%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Georgios A. Konstantopoulos} % Your name at the top

\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'

\moveleft.5\hoffset\centerline{\url{https://gakonst.com} | \url{https://github.com/gakonst} |  \url{https://linkedin.com/in/gakonst} } % Your address
\moveleft.5\hoffset\centerline{\url{me@gakonst.com}}
\moveleft.5\hoffset\centerline{+30 6978832328}
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{EDUCATION}

{\sl M.Eng. Electrical and Computer Engineering}, Aristotle University of Thessaloniki, School of Engineering, Thessaloniki, Greece, expected 2018 \\
\textbf{Relevant Coursework:} Electronics, Electrical Circuits, Software Engineering, Data Structures, Structured/Object-Oriented Programming, Algorithms, Robotics, Controls, Microcontrollers, Operating/Distributed/Embedded Systems, Signal/Image Processing
%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------
\section{TECHNOLOGY \\ SKILLS} 

\textbf{Programming Languages:} Python, Solidity, Matlab, C, C++, Java \\
\textbf{Operating Systems:} Windows, Linux (comfortable with multiple flavors)\\
\textbf{Other:} Penetration Testing, Computer Networks, Raspberry Pi, Arduino

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{EXPERIENCE}

{\sl Independent Smart Contract Auditor} \hfill March 2017-Present
\begin{itemize} \itemsep -2pt % Reduce space between items
    \item Auditing of smart contracts including ICOs, Tokens (ERC20, ERC223, ERC721) and Platforms.
    \item Utilizing automated tooling and scripting for detection of well-known vulnerabilities as well as advising on best practices and optimizations.
\end{itemize}

{\sl Researcher and Technical Writer} \hfill October 2017-Present \\
\textbf{Loom Network} \hfill \url{https://loomx.io}
\begin{itemize} \itemsep -2pt % Reduce space between items
    \item Performing research on blockchain scalability.
    \item Implementing Plasma for scaling Ethereum through sidechains.
    \item Writing articles on blockchain fundamentals, security and scalability.
\end{itemize}

{\sl Software Engineering Intern} \hfill July 2017-December 2017\\
\textbf{Honda R\&D Germany} \hfill \url{http://www.honda.de}
\begin{itemize} \itemsep -2pt % Reduce space between items
    \item Researched blockchain applications on energy markets. 
    \item Developed and tested proprietary smart contracts (tools: Solidity, Truffle Framework, OpenZeppelin, Ganache, Web3.js, Web3.py).
    \item Developed secure cryptographic key generation for IoT devices and interacted with REST APIs in Python.
    \item Managed and set up server for prototyping and local network deployment.
\end{itemize}

{\sl Founder} \hfill January 2017-June 2017 \\
\textbf{ThessSec} \hfill \url{https://github.com/ThessSec}
\begin{itemize} \itemsep -2pt % Reduce space between items
    \item Organized bi-weekly meetups on information security and privacy.
    \item Presented talks on Bitcoin, Web Application Penetration Testing, Network Security (among others).
    \item Educated attendees by leading discussions and interactive workshops.
\end{itemize}

%  {\sl Co-Founder | Software Engineering } \hfill February 2016 - September 2016 \\
%  \textbf{Project M.A.R.T.I.S.}, Thessaloniki Greece
%  \begin{itemize} \itemsep -2pt % Reduce space between items
%  \item Created a wearable device and an Android application, which communicate via Bluetooth, that informs the user on possible dehydration, overexposure to the sun and fever through sensors connected to an Arduino board.
%  \item  Our team qualified to the finals of the panhellenic ECE students’ conference (ECESCON) Hackathon
%  \end{itemize}
%  \section{OTHER}
\textbf{Professional:}
Writing on security and blockchain at \url{https://medium.com/@gakonst}, % (Top writer in Bitcoin) 
IEEE Member \& Event Organizer, attending conferences and local meetups whenever possible.\\
\textbf{Misc. Interests:}
Autonomous Vehicles, Cybersecurity and Privacy, Blockchain, Internet of Things, Wearables, Boxing, Blues Guitar\\
\textbf{MOOCs}:
Cryptography I, Machine Learning by Stanford University, Using Python for Research by Harvard University\\
\textbf{Languages:}
Greek, English, Japanese, French  


% \section{HONORS \& AWARDS}
% \begin{itemize} \itemsep -2pt % Reduce space between items
% \item Most voted idea at The Millennium Project - 2050 Work/Technology Scenarios, December 2016: Cyclic Economy and The end of traditional entrepreneurship
% \item 3rd place in the European BEST Engineering Competition, Case Study Local Round (EBEC) with the presentation: “An approach towards a sustainable transportation % system for Thessaloniki”
% \end{itemize}
% 
% {\sl Social Media and Communications Manager} \hfill November 2016-Present \\
% \textbf{Zero Fuel}, Thessaloniki Greece \hfill facebook.com/0fuel | zerofuel.meng.auth.gr
% \begin{itemize} \itemsep -2pt % Reduce space between items
% \item Maintaining the team's social media platforms
% \item Creating content that promotes the team's sponsors while attracting new ones
% \end{itemize}
% {\sl Steering Committee | Software Engineering } \hfill August 2015 - November 2016 \\
% \textbf{WAVE Academic Expo}, Thessaloniki Greece \hfill wave.afixis.org
% \begin{itemize} \itemsep -2pt % Reduce space between items
% \item Co-organized a scientific exposition addressed to students of all scientific fields
% \item Created software that enabled the efficient management of the particpants and the automated creation of the conference's badges.
% \end{itemize}


%----------------------------------------------------------------------------------------

\end{document}
